Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-01-28 writing/ehp_figures.tex
Work some on formatting

\begin{figure}%[tbhp]
\centering
\includegraphics[width=16cm]{ivanonly.pdf}
\caption{Counties classified as exposed to Hurricane Ivan (2004) under each
exposure metric (Table~1). The red line shows the track of Hurricane Ivan 
based on the revised Atlantic hurricane database \ac{HURDAT2}~\citep{landsea2013}.
Similar maps for other large-extent storms are given in Figure~S3.}
\label{fig:ivanexposure} 
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering 
\includegraphics[width = 0.6\linewidth]{jaccard_heatmap.pdf} 
\caption{Heatmap of Jaccard index values for specific exposure metric pairs
within storms. Only storms between~1996 and~2011, and for which at least~250
counties were exposed based on at least one metric, are included. The color of
each cell within the main heatmap indicates the value of the Jaccard index
(proportion of counties classified as exposed by both metrics out of storms
classified as exposed by either metric) for a given pair of metrics for a given
storm. Storms are displayed within clusters that have similar patterns in
county-level exposure agreement for metric pairs, based on hierarchical
clustering using the complete link method~\citep{murtagh2012algorithms} (i.e.,
storms in the same cluster tend to have similar patterns for the pairwise
strength of agreement among metrics); columns are also ordered based on
hierarchical clustering. The colors to the right of the main heatmap for each
storm indicate the total number of counties classified as exposed to the storm
by any of the five metrics, providing an estimate of storm extent. Maps are
available showing the counties identified as exposed under each of five metrics
for the widest-extent storm in each cluster: Hurricane Ivan (2004)
(Figure~\ref{fig:ivanexposure}) and Hurricanes Floyd (1999), Lee (2011), Cindy
(2005), and Katrina (2005) (Figure~S3).} 
\label{fig:jaccard}
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering
\includegraphics[width=15cm]{averageexposureonly.pdf} 
\caption{Average number of storm exposures per decade in U.S. counties for each
exposure metric. The criteria behind each of the five metrics is given in Table
\ref{tab:exposuremetrics}. The years used to estimate these averages are based
on years of available exposure data (distance and wind:~1988\,--\,2015; rain:
1988\,--\,2011; flood and tornado:~1996\,--\,2015). Similar patterns persist when
analysis is restricted to years with all exposure data available (1996\,--\,2011;
Figure~S5).} 
\label{fig:averageexposure} 
\end{figure}

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=15.5cm]{topelecdependexposure}
\caption{Counties with the highest estimated physical exposure among
electricity-dependent Medicare beneficiaries exposed to storms per year in U.S.
counties for each exposure metric. The criteria behind each of the five metrics
are given in Table~1 [use ref] and details of the physical exposure
calculation are given in the Methods. The color of each bar indicates the
number of Medicare beneficiaries in the county reliant on electricity-dependent
medical and assistive equipment as of July~2017~\citep{empower}. The length of
each bar shows the average expected number of these electricity-dependent
Medicare beneficiaries exposed to tropical storms per year based on a given
exposure metric.}
\label{fig:topelecdependexposure}
\end{figure*}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.6\linewidth]{windcomparison}
\caption{Comparison of estimated wind categories from modeled sustained wind
speed (as used for the wind exposure metric in the main
text;~\citep{stormwindmodel}) versus sustained wind speed determined from the
revised Atlantic hurricane database \ac{HURDAT2}~\citep{landsea2013}. In
\ac{HURDAT2}, wind radii were available for study storms from~2004\,--\,2015
and gives estimates of the maximum radii to which storm winds of 34~\si{\knot},
50~\si{\knot}, and 64~\si{\knot} extended in each four quadrant of the storm at
each of the 6-\si{\hour} storm track observations. We interpolated this data
to~15-\si{\minute} increments and assessed a county as exposed to winds at or above
one of these cutoffs if its population mean center was within~85\% of the
maximum radius for that wind speed in its quadrant of the storm. For each
county in each of the available storms, we also calculated the modeled wind
speed~\citep{stormwindmodel} and then categorized this value into the same
categories available for the \ac{HURDAT2} wind radii ($<$34~\si{\knot};
34\,--\,49.9~\si{\knot}; 50\,--\,63.9~\si{\knot}; $\ge$64~\si{\knot}). Each
point in this graph shows, for a storm, the percent of counties in which the
wind category ($<$34~\si{\knot}; 34\,--\,49.9~\si{\knot};
50\,--\,63.9~\si{\knot}; $\ge$64~\si{\knot}) was the same based on both modeled
winds and the \ac{HURDAT2} wind radii. Only storms with at least one county
with sustained wind of~$\ge$34 \si{\knot}, based on the \ac{HURDAT2} wind
radii, are shown. Hurricanes Sandy (2012) and Ike (2008) were he two storms
with the worst agreement between these two sets of wind data; maps with further
comparisons between the two data sources for these two storms are given in
Figure~\ref{fig:windexamples}.}
\label{fig:windcomparison}
\end{figure}

\begin{figure}[tbhp!] \centering
\includegraphics[width=0.9\linewidth]{raincomparison} \caption{Comparison of
county-level rain exposure based on the reanalysis data used for exposure
assessment in this study \ac{NLDAS-2}~\citep{rui2013nldas,
alhamdan2014environmental} and ground-based weather
stations~\citep{menne2012overview, rnoaa, countyweather}. Each small graph
shows a sample county, and each point on the graph represents a tropical storm
that came within~500 \si{\kilo\metre} of the population mean center of the county.
The x-axis shows the estimated cumulative rainfall (in millimeters) from two
days before to one day after the storm's closest approach to the county based
on the county-aggregated \ac{NLDAS-2} recipitation data used to measure rain
exposure in our main analysis. The ground-based observations (y-axis) are based
on collecting precipitation data from available weather stations in the county,
1988\,--\,2011, summed over the same period from two days before to one day
after the storm's closest approach for each available station. These cumulative
station-based precipitation totals were then averaged across all available
stations in the county to create a county-wide estimate of cumulative
storm-related precipitation for each storm in the county. Horizontal and
vertical lines show the threshold used to classify a storm as exposed based on
cumulative rainfall; storms in the lower left and upper right quadrants are
classified the same regardless of whether reanalysis or station-based
precipitation data is considered, while storms in the upper left and lower
right quadrants would be classified differently. The number of storms within
each county and the average number of stations reporting rainfall during the
county's storms are given above each plot. Note that x- and y-axis ranges
differ by county. An estimate of the rank correlation
(Spearman's~$\rho$~\citep{spearman1904proof}) between measurements from the two
rain data sources is also shown on each graph.} \label{fig:raincomparison}
\end{figure}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.8\linewidth]{floodcomparison}
\caption{Comparison of for a sample of study counties of flood status, based on
NOAA Storm Events listings~\citep{stormevents, noaastormevents}, with total
streamflows at county streamflow gages during tropical storms~\citep{usgsgages,
countyfloods, dataRetrieval}. Each panel represents a separate county. For each
county, we first identified all streamflow gages in the county that had
complete data for Jan.~1~1996\,--\,Dec.~31,~2015. The number of streamflow
gages meeting this criterion are given in parentheses beside the county's name
in the panel title. This analysis covered tropical storm that came
within~500~\si{\kilo\metre} of each sample county between~1996 and~2015. In the
graphs, each point represents a single tropical storm, and the point's position
along the x-axis shows the highest daily total streamflow (cubic feet /
second), summed across all identified streamgages in the county, for a five-day
window centered on the day of the storm's closest approach to the county. The
y-axis separates storms for which a flood event was reported in NOAA's Storm
Events database for the county with a start date within the five-day window of
the storm's closest approach to the county~\citep{stormevents,
noaastormevents}. Boxplots are added to show the distribution of the total
streamflow measurements across storms in the county for storms grouped by
whether or not they were linked with a flood event based on the NOAA Storm
Events data. The color of each point gives the percent of streamflow gages in
the county with a daily streamflow that exceeded a threshold of flooding (the
streamgage's median value for annual peak flow~\citep{countyfloods}) on any day
during the five-day window.  Note that the x-axis scales differ by county,
depending on the number of streamflow gages and typical flow rates for each
gage, and are on a log-10 scale.}
\label{fig:floodcomparison}
\end{figure}

>>>>

\begin{figure}%[tbhp]
\centering
\includegraphics[width=16cm]{ivanonly.pdf}
\caption{Counties classified as exposed to Hurricane Ivan (2004) under each
exposure metric (Table~1). The red line shows the track of Hurricane Ivan 
based on the revised Atlantic hurricane database \ac{HURDAT2}~\parencite{landsea2013}.
Similar maps for other large-extent storms are given in Figure~S3\todo[inline]{Check fig ref}.}
\label{fig:ivanexposure} 
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering 
\includegraphics[width = 0.6\linewidth]{jaccard_heatmap.pdf} 
\caption{Heatmap of Jaccard index values for specific exposure metric pairs
within storms. Only storms between~1996 and~2011, and for which at least~250
counties were exposed based on at least one metric, are included. The color of
each cell within the main heatmap indicates the value of the Jaccard index
(proportion of counties classified as exposed by both metrics out of storms
classified as exposed by either metric) for a given pair of metrics for a given
storm. Storms are displayed within clusters that have similar patterns in
county-level exposure agreement for metric pairs, based on hierarchical
clustering using the complete link method~\parencite{murtagh2012algorithms} (i.e.,
storms in the same cluster tend to have similar patterns for the pairwise
strength of agreement among metrics); columns are also ordered based on
hierarchical clustering. The colors to the right of the main heatmap for each
storm indicate the total number of counties classified as exposed to the storm
by any of the five metrics, providing an estimate of storm extent. Maps are
available showing the counties identified as exposed under each of five metrics
for the widest-extent storm in each cluster: Hurricane Ivan (2004)
(Figure~\ref{fig:ivanexposure}) and Hurricanes Floyd (1999), Lee (2011), Cindy
(2005), and Katrina (2005) (Figure~S3\todo[inline]{Check fig ref}).} 
\label{fig:jaccard}
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering
\includegraphics[width=15cm]{averageexposureonly.pdf} 
\caption{Average number of storm exposures per decade in U.S. counties for each
exposure metric. The criteria behind each of the five metrics is given in Table
\ref{tab:exposuremetrics}. The years used to estimate these averages are based
on years of available exposure data (distance and wind:~1988\,--\,2015; rain:
1988\,--\,2011; flood and tornado:~1996\,--\,2015). Similar patterns persist when
analysis is restricted to years with all exposure data available (1996\,--\,2011;
Figure~S5\todo[inline]{Check fig ref}).} 
\label{fig:averageexposure} 
\end{figure}

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=15.5cm]{topelecdependexposure}
\caption{Counties with the highest estimated physical exposure among
electricity-dependent Medicare beneficiaries exposed to storms per year in U.S.
counties for each exposure metric. The criteria behind each of the five metrics
are given in Table~1 [use ref] and details of the physical exposure
calculation are given in the Methods. The color of each bar indicates the
number of Medicare beneficiaries in the county reliant on electricity-dependent
medical and assistive equipment as of July~2017~\parencite{empower}. The length of
each bar shows the average expected number of these electricity-dependent
Medicare beneficiaries exposed to tropical storms per year based on a given
exposure metric.}
\label{fig:topelecdependexposure}
\end{figure*}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.6\linewidth]{windcomparison}
\caption{Comparison of estimated wind categories from modeled sustained wind
speed (as used for the wind exposure metric in the main
text;~\parencite{stormwindmodel}) versus sustained wind speed determined from
\ac{HURDAT2}~\parencite{landsea2013}. In \ac{HURDAT2}, wind radii were
available for study storms from~2004\,--\,2015 and gives estimates of the
maximum radii to which storm winds of 34~\si{\knot}, 50~\si{\knot}, and
64~\si{\knot} extended in each four quadrant of the storm at each of the
6-\si{\hour} storm track observations. We interpolated this data
to~15-\si{\minute} increments and assessed a county as exposed to winds at or
above one of these cutoffs if its population mean center was within~85\% of the
maximum radius for that wind speed in its quadrant of the storm. For each
county in each of the available storms, we also calculated the modeled wind
speed~\parencite{stormwindmodel} and then categorized this value into the same
categories available for the \ac{HURDAT2} wind radii ($<$34~\si{\knot};
34\,--\,49.9~\si{\knot}; 50\,--\,63.9~\si{\knot}; $\ge$64~\si{\knot}). Each
point in this graph shows, for a storm, the percent of counties in which the
wind category ($<$34~\si{\knot}; 34\,--\,49.9~\si{\knot};
50\,--\,63.9~\si{\knot}; $\ge$64~\si{\knot}) was the same based on both modeled
winds and the \ac{HURDAT2} wind radii. Only storms with at least one county
with sustained wind of~$\ge$34 \si{\knot}, based on the \ac{HURDAT2} wind
radii, are shown. Hurricanes Sandy (2012) and Ike (2008) were he two storms
with the worst agreement between these two sets of wind data; maps with further
comparisons between the two data sources for these two storms are given in
Figure~\ref{fig:windexamples}\todo[inline]{Fix fig ref}.}
\label{fig:windcomparison}
\end{figure}

\begin{figure}[tbhp!] \centering
\includegraphics[width=0.9\linewidth]{raincomparison} \caption{Comparison of
county-level rain exposure based on the reanalysis data used for exposure
assessment in this study \ac{NLDAS-2}~\parencite{rui2013nldas,
alhamdan2014environmental} and ground-based weather
stations~\parencite{menne2012overview, rnoaa, countyweather}. Each small graph
shows a sample county, and each point on the graph represents a tropical storm
that came within~500 \si{\kilo\metre} of the population mean center of the county.
The x-axis shows the estimated cumulative rainfall (in millimeters) from two
days before to one day after the storm's closest approach to the county based
on the county-aggregated \ac{NLDAS-2} recipitation data used to measure rain
exposure in our main analysis. The ground-based observations (y-axis) are based
on collecting precipitation data from available weather stations in the county,
1988\,--\,2011, summed over the same period from two days before to one day
after the storm's closest approach for each available station. These cumulative
station-based precipitation totals were then averaged across all available
stations in the county to create a county-wide estimate of cumulative
storm-related precipitation for each storm in the county. Horizontal and
vertical lines show the threshold used to classify a storm as exposed based on
cumulative rainfall; storms in the lower left and upper right quadrants are
classified the same regardless of whether reanalysis or station-based
precipitation data is considered, while storms in the upper left and lower
right quadrants would be classified differently. The number of storms within
each county and the average number of stations reporting rainfall during the
county's storms are given above each plot. Note that x- and y-axis ranges
differ by county. An estimate of the rank correlation
(Spearman's~$\rho$~\parencite{spearman1904proof}) between measurements from the two
rain data sources is also shown on each graph.} \label{fig:raincomparison}
\end{figure}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.8\linewidth]{floodcomparison}
\caption{Comparison of for a sample of study counties of flood status, based on
NOAA Storm Events listings~\parencite{stormevents, noaastormevents}, with total
streamflows at county streamflow gages during tropical storms~\parencite{usgsgages,
countyfloods, dataRetrieval}. Each panel represents a separate county. For each
county, we first identified all streamflow gages in the county that had
complete data for Jan.~1~1996\,--\,Dec.~31,~2015. The number of streamflow
gages meeting this criterion are given in parentheses beside the county's name
in the panel title. This analysis covered tropical storm that came
within~500~\si{\kilo\metre} of each sample county between~1996 and~2015. In the
graphs, each point represents a single tropical storm, and the point's position
along the x-axis shows the highest daily total streamflow (cubic feet /
second), summed across all identified streamgages in the county, for a five-day
window centered on the day of the storm's closest approach to the county. The
y-axis separates storms for which a flood event was reported in NOAA's Storm
Events database for the county with a start date within the five-day window of
the storm's closest approach to the county~\parencite{stormevents,
noaastormevents}. Boxplots are added to show the distribution of the total
streamflow measurements across storms in the county for storms grouped by
whether or not they were linked with a flood event based on the NOAA Storm
Events data. The color of each point gives the percent of streamflow gages in
the county with a daily streamflow that exceeded a threshold of flooding (the
streamgage's median value for annual peak flow~\parencite{countyfloods}) on any day
during the five-day window.  Note that the x-axis scales differ by county,
depending on the number of streamflow gages and typical flow rates for each
gage, and are on a log-10 scale.}
\label{fig:floodcomparison}
\end{figure}

### 2019-01-28 writing/ehp_introduction.tex
Work some on formatting

Tropical cyclones, including hurricanes, can have disastrous impacts in the
\ac{US}. A tropical cyclone's high winds can bring health risks
and property damage through structural damage of houses and other buildings,
falling trees, and wind-borne debris~\citep{rappaport2000} and cause power
outages~\citep{liu2005, han2009}, which introduce a number of threats to human
and ecological health, including water quality risks if the outage affects
wastewater treatment plants~\citep{mallin2006}.  Other risks can exist without
severe wind; for example, one study found that most of the direct
hurricane-related deaths in the \ac{US} between~1970 and~1999 occurred in cases
when wind was below hurricane strength, including for Tropical Storms Charley
in~1998 and Alberto in~1994~\citep{rappaport2000}.  Tropical cyclones can
produce excessive rain, especially in certain topographies (e.g., near
mountains), so counties well inland sometimes experience more extreme rain than
coastal counties. Flood risks from tropical cyclones can result from this rain,
although the two risks are not perfectly correlated~\citep{chen2015}. In the
\ac{US}, over half of hurricane-related direct deaths from~1970 to~1999 from
Atlantic basin storms were a result of freshwater flooding~\citep{rappaport2000}. 
Flooding can also degrade water quality~\citep{mallin2006}, which can threaten both 
human and ecological health.

To measure tropical cyclone exposure for either investigations of exposure
patterns or for estimation of tropical cyclone risks and impacts, including
those related to human health, studies have varied widely in how they determine
tropical cyclone exposure (some examples shown in Figure~S1). While some
studies have measured exposure based on specific hazards of the tropical
cyclone (e.g., wind, rain), many have used distance from the tropical
cyclone's central track as a surrogate in identifying exposure to the hazards
of a tropical cyclone (e.g.,~\citet{czajkowski2011, tansel2010, kinney2008,
caillouet2008increase}).

Distance from the tropical cyclone's central track can be easily measured using
widely-available hurricane tracking data. There are, however, a number of
limitations to using distance to assess exposure to tropical cyclones, and
there are reasons to suspect that exposure classifications based on other
tropical cyclone hazards may disagree with distance-based classifications.
Tropical cyclones vary dramatically in size: \ac{US} tropical cyclones have
been observed with radii to maximum winds as small as~20~\si{\kilo\metre} and as
large as~200~\si{\kilo\metre}~\citep{mallin2006, quiring2011variations}. While a
number of tropical cyclone hazards are strongly associated with distance from
the tropical cyclone's center (e.g., wind and, at the coast, storm surge and
waves~\citep{rappaport2000, kruk2010}), other hazards like dangerous rain,
floods, and tornadoes can occur well away from the tropical cyclone's central
track~\citep{rappaport2000, atallah2007, moore2012}.  For example, fatal
tropical cyclone tornadoes, which were linked to over~300 deaths in the \ac{US}
between~1995 and~2009, most often occur~200\,--\,500~\si{\kilo\metre} from the
tropical cyclone's center~\citep{moore2012}.

Further, distance-based exposure metrics that use
buffers tend to use an equal buffer distance on each side of the tropical
cyclone track (e.g.,~\cite{czajkowski2011, grabich2015, grabich2016,
zandbergen2009, tansel2010}), but the forces of a tropical cyclone tend to be
distributed around the center in a non-symmetrical way. For example, extreme
winds are more common to the right of the track, where counter-clockwise
cyclonic winds move in concert with the tropical cyclone's forward 
motion~\citep{halverson2015}, and the fatal tornadoes associated with \ac{US} tropical
cyclones between~1995 and~2009 occurred almost exclusively to the right of the
tropical cyclone's track, mostly in the right front quadrant of the tropical
cyclone~\citep{moore2012}. Rain, conversely, is often heaviest to the left of
the tropical cyclone's track, especially when the tropical cyclone interacts
with other weather systems~\citep{atallah2003, atallah2007, zhu2013variations}
or undergoes an extratropical transition~\citep{elsberry2002}.

[Something about differences in other metrics]

@@

To investigate this, we measured county-level exposure to tropical cyclones in
all eastern \ac{US} counties using five metrics
(Table~\ref{tab:exposuremetrics}): (1)~distance to tropical cyclone track;
(2)~maximum sustained wind speed; (3)~cumulative rainfall; (4)~flood events;
and (5)~tornado events.  We assessed exposure at the county level since data on
many potential impacts are available at county-level aggregations (e.g., direct
hurricane-related deaths~\citep{czajkowski2011}; birth
outcomes~\citep{grabich2015, grabich2016}; autism
prevalence~\citep{kinney2008}) and since decisions and policies to prepare for,
and respond to, tropical cyclones are often undertaken at the county
level~\citep{zandbergen2009, rappaport2000}.  We explored patterns in these
exposure assessments and measured how well exposure classification agreed
across these five metrics in terms of classifying specific counties as exposed
to a tropical cyclone.  Finally, to make this hazard-specific tropical cyclone
exposure data available to other researchers, we published open source software
for county-based hurricane exposure assessment in \ac{US}
counties~\citep{hurricaneexposure}.

>>>>

Tropical cyclones, including hurricanes, can have disastrous impacts in the
\acf{US}. A tropical cyclone's high winds can bring health risks
and property damage through structural damage of houses and other buildings,
falling trees, and wind-borne debris~\parencite{rappaport2000} and cause power
outages~\parencite{liu2005, han2009}, which introduce a number of threats to human
and ecological health, including water quality risks if the outage affects
wastewater treatment plants~\parencite{mallin2006}.  Other risks can exist without
severe wind; for example, one study found that most of the direct
hurricane-related deaths in the \ac{US} between~1970 and~1999 occurred in cases
when wind was below hurricane strength, including for Tropical Storms Charley
in~1998 and Alberto in~1994~\parencite{rappaport2000}.  Tropical cyclones can
produce excessive rain, especially in certain topographies (e.g., near
mountains), so counties well inland sometimes experience more extreme rain than
coastal counties. Flood risks from tropical cyclones can result from this rain,
although the two risks are not perfectly correlated~\parencite{chen2015}. In the
\ac{US}, over half of hurricane-related direct deaths from~1970 to~1999 from
Atlantic basin storms were a result of freshwater flooding~\parencite{rappaport2000}. 
Flooding can also degrade water quality~\parencite{mallin2006}, which can threaten both 
human and ecological health.

To measure tropical cyclone exposure for either investigations of exposure
patterns or for estimation of tropical cyclone risks and impacts, including
those related to human health, studies have varied widely in how they determine
tropical cyclone exposure (some examples shown in Figure~S1\todo{Check
fig.ref}). While some studies have measured exposure based on specific hazards
of the tropical cyclone (e.g., wind, rain), many have used distance from the
tropical cyclone's central track as a surrogate in identifying exposure to the
hazards of a tropical cyclone (e.g.,~\textcite{czajkowski2011, tansel2010,
kinney2008, caillouet2008increase}).

Distance from the tropical cyclone's central track can be easily measured using
widely-available hurricane tracking data. There are, however, a number of
limitations to using distance to assess exposure to tropical cyclones, and
there are reasons to suspect that exposure classifications based on other
tropical cyclone hazards may disagree with distance-based classifications.
Tropical cyclones vary dramatically in size: \ac{US} tropical cyclones have
been observed with radii to maximum winds as small as~20~\si{\kilo\metre} and as
large as~200~\si{\kilo\metre}~\parencite{mallin2006, quiring2011variations}. While a
number of tropical cyclone hazards are strongly associated with distance from
the tropical cyclone's center (e.g., wind and, at the coast, storm surge and
waves~\parencite{rappaport2000, kruk2010}), other hazards like dangerous rain,
floods, and tornadoes can occur well away from the tropical cyclone's central
track~\parencite{rappaport2000, atallah2007, moore2012}.  For example, fatal
tropical cyclone tornadoes, which were linked to over~300 deaths in the \ac{US}
between~1995 and~2009, most often occur~200\,--\,500~\si{\kilo\metre} from the
tropical cyclone's center~\parencite{moore2012}.

Further, distance-based exposure metrics that use
buffers tend to use an equal buffer distance on each side of the tropical
cyclone track (e.g.,~\cite{czajkowski2011, grabich2015, grabich2016,
zandbergen2009, tansel2010}), but the forces of a tropical cyclone tend to be
distributed around the center in a non-symmetrical way. For example, extreme
winds are more common to the right of the track, where counter-clockwise
cyclonic winds move in concert with the tropical cyclone's forward 
motion~\parencite{halverson2015}, and the fatal tornadoes associated with \ac{US} tropical
cyclones between~1995 and~2009 occurred almost exclusively to the right of the
tropical cyclone's track, mostly in the right front quadrant of the tropical
cyclone~\parencite{moore2012}. Rain, conversely, is often heaviest to the left of
the tropical cyclone's track, especially when the tropical cyclone interacts
with other weather systems~\parencite{atallah2003, atallah2007, zhu2013variations}
or undergoes an extratropical transition~\parencite{elsberry2002}.

\todo[inline]{Something about difference in other metrics}

@@

To investigate this, we measured county-level exposure to tropical cyclones in
all eastern \ac{US} counties using five metrics
(Table~\ref{tab:exposuremetrics}): (1)~distance to tropical cyclone track;
(2)~maximum sustained wind speed; (3)~cumulative rainfall; (4)~flood events;
and (5)~tornado events.  We assessed exposure at the county level since data on
many potential impacts are available at county-level aggregations (e.g., direct
hurricane-related deaths~\parencite{czajkowski2011}; birth
outcomes~\parencite{grabich2015, grabich2016}; autism
prevalence~\parencite{kinney2008}) and since decisions and policies to prepare for,
and respond to, tropical cyclones are often undertaken at the county
level~\parencite{zandbergen2009, rappaport2000}.  We explored patterns in these
exposure assessments and measured how well exposure classification agreed
across these five metrics in terms of classifying specific counties as exposed
to a tropical cyclone.  Finally, to make this hazard-specific tropical cyclone
exposure data available to other researchers, we published open source software
for county-based hurricane exposure assessment in \ac{US}
counties~\parencite{hurricaneexposure}.
